Replication of \"Anti-Immigrant Rhetoric and ICE Reporting Interest: Evidence

### 2024-06-28 paper_replication_buka.Rmd
paper replication with attempted extensions

```{r}
google_term_data |> 
  ggplot(aes(x = ymd, y= immigr_report, colour = president)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Time Line") +
  ylab("Immigration Report Search Trend") +
  ggtitle("Immigration Report Search Trend on Google Trend Data")
```
```{r}
google_term_data |> 
  ggplot(aes(x = ymd, y= immigr_crime, colour = president)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Time Line") +
  ylab("Immigration Crime Search Trend") +
  ggtitle("Immigration Crime Search Trend on Google Trend Data")
```

@@

head(google_term_data_dummies)
```
```{r}
model_crime <- lm(immigr_crime ~ (ymd + president_bush + president_trump + president_obama), data = google_term_data_dummies)
model_welfare <- lm(immigr_welfare ~ (ymd + president_bush + president_trump + president_obama), data = google_term_data_dummies)
model_report <- lm(immigr_report ~ (ymd + president_bush + president_trump + president_obama ), data = google_term_data_dummies)

```
```{r}
stargazer(model_crime, model_welfare, model_report,
          title = "Table 3 OLS",
          dep.var.labels = c("Crime", "Welfare", "Report"),

@@

# Figure 2 from paper
```{r}
library(stm)
load("from_replication_files/TopicModel.RData")
document_topics <- make.dt(immigrFit, meta = out$meta)
topic_terms <- t(exp(immigrFit$beta$logbeta[[1]]))
rownames(topic_terms) <- out$vocab
colnames(topic_terms) <- sprintf("Topic%d", 1:ncol(topic_terms))
```
```{r}
document_topics_figure <- document_topics |>
  mutate(date = as.Date(date),
         year_month = ym(format(date, "%Y-%m")))
```

@@

@@

>>>>

```{r}
google_term_data |> 
  ggplot(aes(x = ymd, y= immigr_report, colour = president)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Time Line") +
  ylab("Immigration Report Search Trend") +
  ggtitle("Immigration Report Search Trend on Google Trend Data")
```

```{r}
google_term_data |> 
  ggplot(aes(x = ymd, y= immigr_crime, colour = president)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  xlab("Time Line") +
  ylab("Immigration Crime Search Trend") +
  ggtitle("Immigration Crime Search Trend on Google Trend Data")
```

@@

head(google_term_data_dummies)
```

```{r}
model_crime <- lm(immigr_crime ~ (ymd + president_bush + president_trump + president_obama), data = google_term_data_dummies)
model_welfare <- lm(immigr_welfare ~ (ymd + president_bush + president_trump + president_obama), data = google_term_data_dummies)
model_report <- lm(immigr_report ~ (ymd + president_bush + president_trump + president_obama ), data = google_term_data_dummies)

```{r}
stargazer(model_crime, model_welfare, model_report,
          title = "Table 3 OLS",
          dep.var.labels = c("Crime", "Welfare", "Report"),

@@

# Figure 2 from paper
```{r}
library(stm)
load("TopicModel.RData")
document_topics <- make.dt(immigrFit, meta = out$meta)
topic_terms <- t(exp(immigrFit$beta$logbeta[[1]]))
rownames(topic_terms) <- out$vocab
colnames(topic_terms) <- sprintf("Topic%d", 1:ncol(topic_terms))
```

```{r}
document_topics_figure <- document_topics |>
  mutate(date = as.Date(date),
         year_month = ym(format(date, "%Y-%m")))
```

@@

set.seed(1)

searches <-
  read_csv("C:/Users/buka/Documents/coursework/week4/immigrants.csv", skip = 3, col_names = c("month", "report", "crime", "welfare"))

adj <-
  read_csv("C:/Users/buka/Documents/immigrants/immigrant-news-2024-group-1/from_replication_files/gt_report_daily.csv") %>%
  rename(ymd = date)

month_model_data <-
  document_topics_figure %>%
  group_by(year_month) %>%
  summarize(
    segs = n(),
    crime_prop = sum(Topic1) + sum(Topic3),
    welfare_prop = sum(Topic13)
  ) %>%
  rename(ymd = year_month) %>%
  left_join(google_term_data_dummies)

day_model_data <-
  document_topics_figure %>%
  mutate(
    segs = n(),
    crime_prop = Topic1 + Topic3,
    welfare_prop = Topic13
  ) %>%
  rename(ymd = date) %>%
  left_join(adj) %>%
  mutate(president_trump = ifelse(ymd >= "2017-01-20", 1, 0))

model_month <- lm(immigr_report ~
              segs +
              crime_prop +
              welfare_prop +
              ymd +
              president_trump, 
            data = month_model_data)

model_day <- lm(search_adj ~
              segs +
              crime_prop +
              welfare_prop +
              ymd +
              president_trump, 
            data = day_model_data)

@@

```{r}
stargazer(model_month,
          title = "Table 4 OLS Monthly",
          dep.var.labels = c("Report"),
          out = "table4_ols.html", # Save to HTML file
          type = "text", # You can also use "html" or "latex"
          intercept.bottom = FALSE,
          omit.stat = c("ser", "adj.rsq", "f", "aic"),
          notes = "Note: ∗p<0.1; ∗∗p<0.05; ∗∗∗p<0.01"
)

stargazer(model_day,
          title = "Table 4 OLS Daily",
          dep.var.labels = c("Report"),
          out = "table4_ols.html", # Save to HTML file
          type = "text", # You can also use "html" or "latex"
          intercept.bottom = FALSE,
          omit.stat = c("ser", "adj.rsq", "f", "aic"),
          notes = "Note: ∗p<0.1; ∗∗p<0.05; ∗∗∗p<0.01"
)
```

--- POSSIBLE EXTENTION QUESTIONS ---
do different news outlets have stronger or weaker effects on searches ?

maybe people want to move if they believe illegal immigrant population is high ? - (housing data ?)
  or how do reports about immigrant crime etc wffect people moving (topic 27, 3, 1)

do people really act with ice reportings ? is it reflected in anti-immigrant searches ? - (ice data)
  (test statement that "First, at least some searches for ‘how to report an immigrant’ will likely      result in an actual denunciation.")

which states have the highest suspicion of immigrants (highest searches) and which states did trump     win the majority ? is there a correlation ?

trump_votes <-
  read_csv("elections_2016.csv", skip = 4, col_names = c("state", "", "", "votes", "", "", "state_total")) %>%
  select(state, votes, state_total) %>%
  head(-7) %>%
  rename(state_abb = state)

report_searches <-
  read_csv("report_popularity.csv", skip = 3, col_names = c("state", "searches")) %>%
  mutate(state_abb = state.abb[match(state, state.name)])
report_searches[1, 3] <- "DC"

data_by_state <-
  trump_votes %>%
  left_join(report_searches, by="state_abb") %>%
  mutate(votes = as.numeric(gsub(",", "", votes)), perc = votes / state_total, state_abb = as.factor(state_abb))

data_by_state %>%
  ggplot(aes(x = searches, y = perc)) +
  geom_point()

searches_report <-
  read_csv("C:/Users/buka/Documents/immigrants/immigrant-news-2024-group-1/from_replication_files/gt_report_daily.csv")

preelections <-
  document_topics_figure %>%
  left_join(searches_report) %>%
  mutate(yr = year(date), total_news = Topic1 + Topic3 + Topic13) %>%
  filter(yr %in% c(2014, 2015, 2018, 2019)) %>%
  select(date, yr, Topic1, Topic3, Topic13, search_adj, total_news)

preelections %>%
  ggplot(aes(x = total_news, y= search_adj)) + 
  geom_point()
